Kindly Bent to Free Us

### 2018-11-12 kindly/main.tex
Blip.
A bit more structure.
Add a crappy abstract.

\documentclass[sigconf,author]{acmart}\settopmatter{printfolios=true}

@@

@@

\title{Kindly Bent to Free Us}
\maketitle

\begin{figure*}[h]
  \centering
  \input{syntax}
  \caption{Syntax}

  \input{kinds}
  \caption{Kind rules -- $\haskind{P}{\E}{\tau}{k}$ }

  \input{typing}
  \caption{Typing rules -- $\hastype{P}{\E}{e}{\tau}$ }

  \input{semantics}
  \caption{Reduction rules -- $\ered{I}{E}{e}{v}$ }

\end{figure*}

>>>>

\documentclass[manuscript,author]{acmart}

@@

\usepackage{xspace}

@@

\title{Kindly Bent to Free Us}
\begin{abstract}
  System programming often requires to manipulate resources that
  cannot be duplicated such as file system handles, network connections
  or even globally allocated memory.
  Unfortunately such resources are often the root of bugs and security issues
  through use-after-free errors or data races, even in the context
  of programming language traditionally considered safe, such as statically typed
  functional languages.
  Linear and affine type systems propose to forbid such erroneous programming
  patterns by tracking usage of variables through types.

  We present \lang, an extension of ML with a kind system and qualified
  types that allows to track affine types.
  This language supports the defining features of ML family languages:
  an impure, strict functional expression language with complete principal type
  inference and type abstraction through modules.
  Our language do not require any linearity annotation in
  expressions and support common functional idioms.
\end{abstract}

\maketitle

\input{intro}
\input{lang}

\input{infer/infer}
\input{soa}

\bibliography{biblio}
